---
title: "Example: Analysis of Life Expectancy"
author: "Jaclyn Janis"
date: "2019-08-02"
output: html_document
bibliography: library.bib
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(here)
library(ggplot2)
library(tidyverse)
library(pander)
library(stargazer)
library(beepr)

```
## Introduction

The original analysis by Hans Rosling showed that things are getting better [@Rosling2011].

```{r, message=FALSE}
#Read in data
d <- readr::read_csv(here("data/gapminder/raw/gapminder_data.csv"))
```

##Data

The data consist of `r length(unique(d$country))` unique countries tracked from `r range(d$year)[1]` to `r range(d$year)[2]`. Table 1 presents a summary of the variables.

```{r, echo=TRUE}
d %>% 
  group_by(country) %>% 
  summarize(pop = mean(pop),
            lifeExp = mean(lifeExp)) %>% 
  pander()
```

## Results

```{r}
m <- lm(lifeExp ~ continent + year + pop, data= d)

```
```{r, results="asis"}
stargazer(m, type = "html", ci = T)
```


##Analysis of Life Expectancy by Continent

We hypothesize that life expectancy is a function of time and location.


**This is not a real analysis. This is all just an example of RMarkdown.**

[Link to the github respository](https://github.com/jaclynjanis/2019-04-02-carpentries-mmc)


```{r, message = FALSE}

d %>% 
  ggplot(aes(x = year, y = lifeExp, color = continent)) +
  geom_point(alpha = 0.5)
```

You can use R code in line. The data consist of years from `r range(d$year)[1]` to `r range(d$year)[2]` .


## References



